\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Patrick James Pangilinan} \\
  \small 0966-749-7052 ; 0976-339-7093 $|$ \href{mailto:alex@email.com}{patrickjpangilinan@protonmail.com} $|$ 
  \href{https://github.com/zwayth}{github.com/pjpangilinan}
\end{center}

\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: Python, C++, JavaScript, Bash}
  \resumeItem{\textbf{Frameworks \& Tools}: Linux, React, FastAPI, Git, Docker, Postman}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
      {Tech Support Intern}{July 2025 -- September 2025}
      {City Government of Trece Martires -- ICT Division}{Trece Martires City}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Cleaned and verified large-scale digital citizen records from post-2004 archives, improving data accuracy and consistency.}
          \resumeItem{\textbullet\ Supported rollout of a Document Tracking System across multiple departments by assisting in system validation, user onboarding, and issue resolution.}
          \resumeItem{\textbullet\ Troubleshot hardware, software, and network issues across office systems.}
          \resumeItem{\textbullet\ Configured workstations and peripherals to support reliable day-to-day operations for staff.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Part Timer}{2021 -- Present}
      {NLMontano Accounting Firm}{Trece Martires City}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Processed and encoded government remittances, including SSS, PhilHealth, and Pag-IBIG.}
          \resumeItem{\textbullet\ Provided technical support for PCs, printers, and small office networks, including setup, maintenance, and troubleshooting.}
          \resumeItem{\textbullet\ Assisted in maintaining system reliability and resolving technical issues in a small business environment.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
  \resumeSubheading
      {VOTECHAIN: Voting Optimization Through Encrypted Blockchain}{}
      {Python, Raspberry Pi, Blockchain, React, WebSockets}{\href{https://github.com/pjpangilinan/votechain}{github.com/pjpangilinan/votechain}}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Designed and developed a secure electronic voting system using Raspberry Pi and a Python-based blockchain architecture.}
          \resumeItem{\textbullet\ Implemented SHA-256 cryptographic hashing and chained blocks to support tamper-evident, immutable vote records.}
          \resumeItem{\textbullet\ Built a real-time transparency dashboard using React and WebSockets to display live vote counts for public auditing.}
          \resumeItem{\textbullet\ Engineered end-to-end system architecture, including hardware input, local processing, secure storage, and web-based visualization.}
      \resumeSubHeadingListEnd

  \resumeSubheading
      {Up To Date -- AI-Powered News Dashboard}{}
      {React, FastAPI, Groq API, Docker, PWA}{\href{https://github.com/pjpangilinan/tech-dashboard}{github.com/pjpangilinan/tech-dashboard}}
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developed a full-stack web application using React and FastAPI.}
          \resumeItem{\textbullet\ Integrated AI-powered summarization through the Groq API for on-demand content insights.}
          \resumeItem{\textbullet\ Implemented custom RSS feeds, keyboard shortcuts, and Progressive Web App installability.}
          \resumeItem{\textbullet\ Containerized the application using Docker for consistent deployment and scalability.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {Cavite State University}{Bancod, Indang, Cavite}
      {Bachelor of Science in Computer Engineering}{2022 -- 2027}
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingList
  \resumeItem{\textbf{Google Advanced Data Analytics Professional} -- Coursera \hfill May 2025}
  \resumeItem{\hspace*{1.2em}\href{https://coursera.org/share/ea689640b74331ba8237231893ad55be}{coursera.org/share/ea689640b74331ba8237231893ad55be}}

  \resumeItem{\textbf{ISO, CMMI \& Project Quality Certification Mastery} -- Coursera \hfill May 2026}
  \resumeItem{\hspace*{1.2em}\href{https://coursera.org/share/eac46fe83d3208954b2cece33250a40e}{coursera.org/share/eac46fe83d3208954b2cece33250a40e}}
\resumeSubHeadingListEnd

\end{document}
